% !TEX root = WendtPhDThesis.tex
\begin{acknowledgments}

  It was an absolute pleasure to work with Prof.\ Richard Furnstahl.  Even after
  four years of working closely with Dick, I am still in awe of the time and
  effort he invests in his students.  His passion towards physics, dedication
  towards mentorship, and caring about the scientific community is exemplary.
  I certainly consider it a privilege to be his padawan and hope to have
  imbibed at least part of his scientific ethos.

  I am also thankful to my committee members, in particular Robert
  Perry.  Their constructive criticism and feedback has helped me develop
  professionally.  I was fortunate to learn from a few exceptional
  teachers at Ohio State.  I thank them for instilling in me a joy for learning
  advanced physics.  I would like to express my gratitude towards
  Scott Bogner and Thomas Papenbrock; they have been a constant source of
  support, and I look up to them as mentors.  I am grateful to
  Sabine Jeschonnek for helping with the deuteron disintegration theory.
  I have also benefited tremendously from the interactions with professors
  and peers in the wider nuclear physics community.

  My time at Ohio State coincided with some of the best
  post-docs in the group---Heiko, Kai, and Sebastian.  They were always ready
  to help and my PhD experience has
  been enriched immensely through interactions with them.  I have worked
  closest with Sebastian; I admire his efficiency and his attention to details.

  I was also lucky to overlap with excellent fellow graduate students in the group.
  It was fun growing up with my physics siblings---Kyle, Sarah, and Alex.
  Special mention goes to Kyle for doing a great job of an elder sibling.
  It was a pleasure to share office space with Brian, Russell, and Khal.
  I thank them for being a jolly company and for putting up with my
  idiosyncrasies.  The other physics graduate students that I would like
  to acknowledge are my gym buddies Hudson and Chuck and my former officemate
  Omar.  I have enjoyed discussion with them over a full gamut of topics and
  always turned to them for friendly advice when needed.

  My friend Kaushik and I landed in the US together five years ago.  We have had
  a good run as flatmates since then.  From teaching me cooking to being my
  driving
  instructor, I am indebted to him for many things.  One of the best things
  that happened to me at OSU was joining the student group Sankalpa.  I thank
  Gayatri, Vinayak, and Keerthi for getting me started along that path.
  Friends formed through Sankalpa have been like a family to me and have
  helped me grow as a person.  I thank Mithila, Dhruv, and Garima for being
  my safety net; Janani, Pooja, Shubhendu, and Keshav for intellectually
  engaging discussions; and Vipul, Nandan, Subhasree, and Bakul for being
  a lot of fun.

  I would like to take this opportunity to visit my roots and express gratitude
  towards my undergraduate teachers, friends, and relatives back in India.
  They trusted in me when I had little to show.  I value the decade-long
  friendship of my pals Sheetal Kumar, Ajit, Shishir, Vivek, and Lakshmi Priya.

  Finally, I must put on record the unremitting love of my doting yet
  disciplinarian parents and my headstrong but sweet younger sister.
  Their unwavering encouragement through thick and thin keeps me
  going and motivates me to scale new heights.

\end{acknowledgments}
